\chapter{Getting Started}

% Separate section from chapter.
\newpage

\section{Prologue}

\begin{displayquote}
   \textit{Computers aren't very smart.}
\end{displayquote}

\paragraph{}
   Computers are generally very good at math, they can do what you tell them to do and they can assist you in searching the internet, but they aren't
   able to do much beyond that without painstaking, very explicit instructions.

\begin{displayquote}
   \textit{If you asked it to vaccuum the house for you, could it?}
   \textit{If you asked it to draw a picture of a bird for you, would it?}
   \textit{A computer would have no idea what you're saying.}
\end{displayquote}

\paragraph{}
   Computers are generally very bad at understanding things would very specific instructions and even then can't really accomplish a task if given in
   even slightly uncertain terms or if terms are conflated, things can go wrong very easily. They don't understand English, so we often have to adapt
   our understanding of things to fit into another language in order to be able to properly instruct a computer to take on a task in the way that we
   want it to. An example of one such language would be `C', which functions by compiling a higher level set of instructions that we write into
   machine code that the computer can understand.

\paragraph{}
   Machine code can be loosely defined as `binary'. It is a series of zeroes and ones that tell the computer what to do at a very low level. And
   because binary code can be very difficult to write and is very prone to mistakes, higher-level languages like C were created to make it easier to
   tell computers what they need to do. C can still, however, be very painstaking to write for larger scale projects and so other higher-level
   languages were created in order to make certain tasks easier to achieve.

\paragraph{}
   This report was created to explain the basics and some more advances topics in programming and to help you, the Reader, to learn the subject with
   grace and efficiency.

% A \newpage should be placed at the end of every section.
\newpage
